Inverse Problems --- Example Sheet 1

### 2020-11-02 distribution_theory/distribution_ES1.tex
distribution theory is still difficult :((

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=3cm]{geometry}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{mathtools, amsmath, amssymb, amsthm, mathabx, enumerate, mdframed, bbm, graphicx, float, physics, xcolor, cleveref}

@@

\title{Distribution Theory and Applications --- Example Sheet 1} % subject
\author{Lucas Riedstra}
\date{...} % date

@@

@@

\begin{proof}
	Since $\phi \in \DD(X)$, we know that $\supp\phi \subseteq \clos{B_N}$ for some $N \in \NN$. Now, suppose $\norm{h} < 1$, then
	\[
	\phi(x+h) \neq 0 \implies \norm{x + h} \leq N \implies \norm{x} \leq \norm{x + h} + \norm{h} \leq N + 1, 
	\]
	so if we define $\psi_h(x) = \phi(x+h)$ then we know that $\supp\phi_h \subseteq \clos{B_{N+1}}$.

	By Taylor's theorem, we have
	\[
	\phi(x+h) = \sum_{\abs{\alpha} \leq N} \frac{h^\alpha}{\alpha!} \pt^\alpha \phi(x) + R_N(x, h),  
	\]
	and since $\sum_{\abs{\alpha} \leq N} \frac{h^\alpha}{\alpha!} \pt^\alpha \phi(x)$ vanishes for $x \notin \clos{B_N}$, it is clear that $\supp(R_N(\cdot, h))$ must also be contained in $\clos{B_{N+1}}$ (again, for $\norm{h} \leq 1$). This shows that $\supp(R_N)$ is contained in $\clos{B_{N+1}}$ for $\abs{h}$ sufficiently small.

	Now let $\beta$ be a multi-index and define $C \ceq \frac{1}{N!} \max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}$ (note that $C$ exists and is finite since all partial derivatives of $\phi$ have compact support), then we have
	\begin{align*}
	\abs{\pt^\beta R_N(x, h)} &= \abs{\pt^\beta \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1)\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	%&= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \cdot \pt^\beta\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	&\overset\star= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \int_0^1 (1-t)^N (\pt^{\alpha + \beta}\phi)(x + th)\dd{t}} \\
	&\leq \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!}(N+1) \int_0^1 (1-t)^N \abs{\qty(\pt^{\alpha + \beta}\phi)(x+th)} \dd{t} \\
	&\leq \qty[\max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}] \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!} (N+1) \\
	&\leq C (N+1)! \sum_{\abs{\alpha}= N+1}\frac{\abs{h^\alpha}}{\alpha!} = C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}.
\end{align*}
Since this upper bound does not depend on $x$, we also have
\[
\sup_x \abs{\pt^\beta R_N(x, h)} \leq C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}, 
\]
and we conclude that
\[ 
\frac{\sup_x \abs{\pt^\beta R_N(x, h)}}{\norm{h}^N} \leq \frac{C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}}{\norm{h}^N} \leq \frac{C N^{N+1} \norm{h}^{N+1}}{\norm{h}^N} = CN^{N+1} \norm{h} \to 0, 
\]
and therefore that $\pt^\beta R_N(x, h) = o(\norm{h}^n)$ for all multi-indices $\beta$. 
\end{proof}

@@

\begin{solution}
	Let $K \subseteq U_1$. Define $U_2 \ceq U_1 + B(0, 1)$ and let $\chi = \ind_{U_2}$. Now let $\psi \in \DD(\RR^n)$ satisfy $\int_{\RR^n} \psi \dd{x} = 1$ and $\supp\psi \subseteq B(0, 1)$. The we compute
	\begin{align*}
		(\chi * \psi)(x) &= \int_{\RR^n} \chi(y) \psi(x - y) \dd{y} = \int_{U_2} \psi(x - y) \dd{y}.
	\end{align*}
	Clearly, $\chi * \psi \in \DD(X)$, and furthermore, we have for $x \in U_1$ that
	\[
	\int_{U_2} \psi(x - y) \dd{y} = \int_{U_2 - x} \psi(z) \dd{z} \overset\star= 1,
	\]
	since $B(0, 1) \subseteq U_2 - x$. This proves the claim.
\end{solution}

@@

		\item Since $e^{2\pi i x} = 1 \iff x \in \ZZ$, intuitively it must be the case that $u'$ is 0, except ``on $\ZZ$'', whatever that may mean. Therefore, we guess that, for any sequence $(\alpha_n)_{n \in \ZZ} \subseteq \CC$ and constant $c \in \CC$, the map \[u = c + \sum_{n \in \ZZ} \alpha_n \ind_{x \geq n}.\] We compute the derivative of $u$. It is easily seen that $u' = \sum_{n \in \ZZ} \alpha_n \delta_n$ (the infiniteness of the sum does not pose a problem since the test functions are compactly supported, so $\ang{u, \phi}$ will always be a finite sum). 
%		We have for arbirary $\phi$ that
%		\begin{align*}
%		\ang{u', \phi} &= - \ang{u, \phi'} = -\int_\RR \sum_{n \in \ZZ} \qty(\alpha_n \ind_{x \geq n}) \phi'(x) \dd{x}	\overset\star= - \sum_{n \in \ZZ} \alpha_n \int_n^\infty \phi'(x) \dd{x} = \sum_{n \in \ZZ} \alpha_n \phi(n),	
%		\end{align*}
%	where $\star$ follows from the fact that the sum is finite since $\phi'$ is compactly supported. 
%	Therefore, we can conclude $u' = \sum_{n \in \ZZ} \alpha_n \delta_n$, and indeed we find
From this, we see that
	\[
	\ang{(e^{2\pi i x} - 1) u', \phi} = \ang{u', (e^{2\pi i x} -1 )\phi} = \sum_{n \in \ZZ} \alpha_n (e^{2\pi i n} - 1) \phi(n) = 0,
	\]
	so $u$ satisfies the equation. \TODO Why is this the most general solution? Intuitively clear, but how to make this rigorous?
	\end{enumerate}
\end{solution}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[margin=3cm]{geometry}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{mathtools, amsmath, amssymb, amsthm, mathabx, mdframed, bbm, graphicx, float, physics, xcolor, cleveref}

@@

\title{Distribution Theory and Applications --- Example Sheet 1} % subject
\author{Lucas Riedstra}
\date{4 November 2020} % date

@@

\begin{mdframed}
For both questions 2 and 4, we need the following lemma:
\begin{lemma} \label{lem:distance_compact_closed}
	Let $K, V \subseteq \RR^n$ where $K$ is compact, $V$ is closed, and $K \cap V = \emptyset$. Then there is a nonzero distance between $K$ and $V$, i.e., 
	\[
	\inf_{x \in K, v \in V} \norm{x - v} > 0. 
	\]
\end{lemma}

\begin{proof}
	We know that $K \subseteq V\C$ and that $V\C$ is open, so for every $x \in K$ there exists an open ball $B(x, \eps_x)$ around $x$ such that $B(x, 2\eps_x) \subseteq V\C$. Since $\qty{B(x, \eps_x)}$ is an open covering of $K$, there exist finitely many balls $B(x_1, \eps_1), \dotsc, B(x_n, \eps_n)$ that cover $K$. Let $\eps \ceq \min\qty{\eps_1, \dotsc, \eps_n}$ and $x \in K$, then there is an $x_i$ such that $\norm{x - x_i} < \eps$, and since $B(x_i, 2\eps) \subseteq B(x_i, 2\eps_i) \subseteq V\C$ it is clear that $B(x, \eps) \subseteq V\C$ as well.

	We conclude that $B(x, \eps) \subseteq V\C$ for any $x \in K$, and therefore that $\inf\limits_{x \in K, v \in V} \norm{x - v} \geq \eps > 0$. 
\end{proof}
\end{mdframed}

@@

\begin{proof}
	Let $\phi \in \DD(X)$ with $K = \supp\phi$, then by \cref{lem:distance_compact_closed} we know there exists a nonzero distance $d > 0$ between $K$ and $\RR^n \setminus X$. 
	We claim that if $\norm{h} \leq \frac d2$, then 
	\[
	\supp(R_N) \subseteq \qty{x \in X \mid d(x, K) \leq \frac d2} \eqqcolon \hat K,
	\]
	which is clearly a compact set contained in $X$. Indeed, if $\norm{h} \leq \frac d2$ we have
	\[
	\phi(x+h) \neq 0 \implies x + h \in K \implies d(x, K) \leq \norm{h} \leq \frac d2. 
	\]

%	Since $\phi \in \DD(X)$, we know that $\supp\phi \subseteq \clos{B_N}$ for some $N \in \NN$. Now, suppose $\norm{h} < 1$, then
%	\[
%	\phi(x+h) \neq 0 \implies \norm{x + h} \leq N \implies \norm{x} \leq \norm{x + h} + \norm{h} \leq N + 1, 
%	\]
%	so if we define $\psi_h(x) = \phi(x+h)$ then we know that $\supp\phi_h \subseteq \clos{B_{N+1}}$. 
%	
	By Taylor's theorem, we have
	\[
	\phi(x+h) = \sum_{\abs{\alpha} \leq N} \frac{h^\alpha}{\alpha!} \pt^\alpha \phi(x) + R_N(x, h),  
	\]
	and since $\sum_{\abs{\alpha} \leq N} \frac{h^\alpha}{\alpha!} \pt^\alpha \phi(x)$ vanishes for $x \notin K$, it is clear that $\supp(R_N(\cdot, h))$ must be contained in $\hat K$ (for $\norm{h} \leq \frac d2$).

	Now let $\beta$ be a multi-index and define $C \ceq \frac{1}{N!} \max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}$ (note that $C$ exists and is finite since all partial derivatives of $\phi$ have compact support), then we have
	\begin{align*}
	\abs{\pt^\beta R_N(x, h)} &= \abs{\pt^\beta \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1)\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	%&= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \cdot \pt^\beta\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	&\overset\star= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \int_0^1 (1-t)^N (\pt^{\alpha + \beta}\phi)(x + th)\dd{t}} \\
	&\leq \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!}(N+1) \int_0^1 (1-t)^N \abs{\qty(\pt^{\alpha + \beta}\phi)(x+th)} \dd{t} \\
	&\leq \qty[\max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}] \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!} (N+1) \\
	&= C (N+1)! \sum_{\abs{\alpha}= N+1}\frac{\abs{h^\alpha}}{\alpha!} = C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}.
\end{align*}
Here, $\star$ follows from differentiation under the integral sign since the integrand is bounded.

Since this upper bound does not depend on $x$, we also have
\[
\sup_x \abs{\pt^\beta R_N(x, h)} \leq C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}, 
\]
and we conclude that
\[ 
\frac{\sup_x \abs{\pt^\beta R_N(x, h)}}{\norm{h}^N} \leq \frac{C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}}{\norm{h}^N} \leq \frac{C N^{N+1} \norm{h}^{N+1}}{\norm{h}^N} = CN^{N+1} \norm{h} \to 0, 
\]
and therefore that $\pt^\beta R_N(x, h) = o(\norm{h}^n)$ for all multi-indices $\beta$. 
\end{proof}

@@

\begin{solution}
	Let $K \subseteq X$, then by \cref{lem:distance_compact_closed}, there is a nonzero distance $d$ from $K$ to $\RR^n \setminus X$, so we have neighbourhoods
	\[
	U_1 \ceq \qty{u \in X \mid d(u, K) < \frac d4}, \quad U_2 \ceq \qty{u \in X \mid d(u, K) < \frac{3d}{4}}
	\]
	which is an open neighbourhood of $K$ with $\clos U \subseteq X$.

	 Let $\chi = \ind_{U_2}$. Now let $\psi \in \DD(\RR^n)$ satisfy $\int_{\RR^n} \psi \dd{x} = 1$ and $\supp\psi \subseteq B(0, \frac d4)$. The we compute
	\begin{align*}
		(\chi * \psi)(x) &= \int_{\RR^n} \chi(y) \psi(x - y) \dd{y} = \int_{U_2} \psi(x - y) \dd{y}.
	\end{align*}
	Clearly, $\chi * \psi \in \DD(X)$, and furthermore, we have for $x \in U_1$ that
	\[
	\int_{U_2} \psi(x - y) \dd{y} = \int_{U_2 - x} \psi(z) \dd{z} \overset\star= 1,
	\]
	since $\supp\psi \subseteq B(0, \frac d4) \subseteq U_2 - x$. This proves the claim.
\end{solution}

@@

		\item Since $e^{2\pi i x} = 1 \iff x \in \ZZ$, it is clear that $\supp(u') \subseteq \ZZ$. We will show that this is also sufficient, i.e., that any distribution $u$ with $\supp(u') \subseteq \ZZ$ yields a solution.

		It is easily seen that 
		\begin{align*}
		\supp(u') \subseteq  \ZZ &\iff u' = \sum_{n \in \ZZ} \alpha_n \delta_n \quad\text{for some $(\alpha_n)_{n \in \ZZ} \subseteq \CC$} \\
		&\iff u = c + \sum_{n\in \ZZ} \alpha_n \ind_{x \geq n} \quad\text{for some $c \in \CC$, $(\alpha_n)_{n \in \ZZ} \subseteq \CC$}. 
		\end{align*}

		Indeed, if $u = c + \sum_{n \in \ZZ} \alpha_n \ind_{x \geq n}$ then 
		\[
		\ang{u', \phi} = -\ang{u, \phi'} \overset\star= - \alpha_n \sum_{n \in \ZZ \cap \supp\phi} \int_n^\infty \phi'(x) \dd{x} = \sum_{n \in \ZZ \cap \supp\phi} \alpha_n \phi(n) = \ang{\sum_{n \in \ZZ} \alpha_n\delta_n, \phi}, 
		\]
		where $\star$ follows from the fact that there are only finitely many $n$ in $\ZZ \cap \supp\phi$ (since $\phi$ has compact support).

%		Therefore, we guess that, for any sequence $(\alpha_n)_{n \in \ZZ} \subseteq \CC$ and constant $c \in \CC$, the map \[u = c + \sum_{n \in \ZZ} \alpha_n \ind_{x \geq n}.\] We compute the derivative of $u$. It is easily seen that $u' = \sum_{n \in \ZZ} \alpha_n \delta_n$ (the infiniteness of the sum does not pose a problem since the test functions are compactly supported, so $\ang{u, \phi}$ will always be a finite sum). 
%		We have for arbirary $\phi$ that
%		\begin{align*}
%		\ang{u', \phi} &= - \ang{u, \phi'} = -\int_\RR \sum_{n \in \ZZ} \qty(\alpha_n \ind_{x \geq n}) \phi'(x) \dd{x}	\overset\star= - \sum_{n \in \ZZ} \alpha_n \int_n^\infty \phi'(x) \dd{x} = \sum_{n \in \ZZ} \alpha_n \phi(n),	
%		\end{align*}
%	where $\star$ follows from the fact that the sum is finite since $\phi'$ is compactly supported. 
%	Therefore, we can conclude $u' = \sum_{n \in \ZZ} \alpha_n \delta_n$, and indeed we find
Finally, we compute that 
	\[
	\ang{(e^{2\pi i x} - 1) u', \phi} = \ang{u', (e^{2\pi i x} -1 )\phi} = \sum_{n \in \ZZ} \alpha_n (e^{2\pi i n} - 1) \phi(n) = 0,
	\]
	so $u$ satisfies the equation. 
	\end{enumerate}
\end{solution}

### 2020-11-02 inverse_problems/C3.tex
distribution theory is still difficult :((

@@

\begin{definition}
	A functional $E$ is called \emph{absolutely one-homogeneous} if $E(\lambda u) = \abs{\lambda} E(u)$ for all $\lambda \in \RR, u \in \XX$. 
\end{definition}

@@

\begin{theorem}[Direct method]
	Let $\XX$ be Banach and $\tau_\XX$ a topology on $\XX$ such that any bounded sequence in $\XX$ has a $\tau_\XX$ convergent subsequence. Then any proper, bounded from below, coercive, $\tau_X$-LSC functional has a minimiser.  
\end{theorem}

@@

>>>>

\begin{lemma} \label{lem:lsc_closed_sets}
	Let $E \colon \XX \to \rext$ be $\tau_\XX$-LSC and $a \in \RR$. Then $\qty{u \in \XX \mid E(u) \leq a}$ is $\tau_\XX$-closed. 
\end{lemma}

\begin{proof}
	Let $(u_n) \overset\tau\to u$ and suppose $E(u_n) \leq a$ for all $n$. Then clearly $E(u) \leq \liminf E(u_n) \leq a$. 
\end{proof}

@@

\begin{definition}
	For $p > 0$, a functional $E$ is called \emph{absolutely $p$-homogeneous} if $E(\lambda u) = \abs{\lambda}^p E(u)$ for all $\lambda \in \RR, u \in \XX$. 
\end{definition}

@@

\begin{theorem}[Direct method] \label{thm:direct_method}
	Let $\XX$ be Banach and $\tau_\XX$ a topology on $\XX$ such that any bounded sequence in $\XX$ has a $\tau_\XX$ convergent subsequence. Then any proper, bounded from below, coercive, $\tau_X$-LSC functional has a minimiser.  
\end{theorem}

@@

\subsection{Regularisation properties}
We consider the problem $Au = f$ where $A \in \BB(\XX, \YY)$ and where $\YY$ is a Banach space and $\XX$ is the dual of a separable Banach space.  Recall that in Tychonoff regularisation, we have
\[
R_\alpha(f_\delta) = \argmin_{u \in \XX} \norm{Au - f_\delta}^2 + \alpha \norm{u}^2. 
\]
Here, the term $\norm{u}^2$ is known as the \emph{regularisation term}, and penalising large values of $\norm{u}$ ensures regularity of the solution. Inspired by this, suppose we have any function $\JJ(u)$ as regulariser, then the \emph{variational regularisation problem} is given by
\[
R_\alpha f_\delta \in \argmin_{u \in \XX} \frac12 \norm{Au - f_\delta}^2 + \alpha \JJ(u), 
\]
\begin{definition}
	Let $u_\JJ\D$ be a least-squares solution that minimises $\JJ$ over all least-squares solutions. Then we call $u_\JJ\D$ a \emph{$\JJ$-minimising solution} of the problem $Au = f$. 
\end{definition}

\begin{convention}
	We will assume there exists t least one least-squares solution with a finite value of $\JJ$. 
\end{convention}

\begin{lemma} \label{lem:null_space_subspace}
	Let $\JJ(u) \ceq \sum_{i=1}^n \JJ_i(u)$, where each $\JJ_i(u)$ is convex and absolutely $p_i$-homogeneous ($p_i > 0$). Then $\Nul(J)$ is a linear subspace of $\XX$. 
\end{lemma}

\begin{proof}
	We note that $\JJ_i$ is nonnegative, since
	\[
	0 = \JJ_i(0) = \JJ_i\qty(\frac12 u - \frac12 u) \leq \frac12\JJ_i(u) + \frac12\JJ_i(-u) = \JJ_i(u).
	\]
	Therefore we have $\Nul(\JJ) = \cap_i \Nul(\JJ_i)$, and we will show that every $\Nul(\JJ_i)$ is a subspace. Let $\lambda \in \RR, u, v \in \Nul(\JJ_i)$, then 
	\[
	\JJ_i(\lambda u + v) = 2^{p_i} \JJ_i\qty(\frac{\lambda u}{2} + \frac v2) \leq 2^{p_i - 1} \qty(\abs{\lambda}^{p_i} \JJ_i(u) + \JJ_i(v)) = 0. 
	\]
	so $\lambda u + v \in \Nul(\JJ_i)$. This completes the proof. 
\end{proof}

\begin{lemma}
	Let the assumptions of \cref{lem:null_space_subspace} be satisfied, and suppose $u \in \XX, v \in \Nul(\JJ)$. Then $\JJ(u + v) = \JJ(u)$. 
\end{lemma}

\begin{proof}
	Clearly it suffices to prove this lemma for each $\JJ_i$. It is easily seen that for any $t \in (0, 1)$ we have
	\[
	\JJ_i(u + v) = \JJ_i \qty(t \frac ut + (1-t) \frac{v}{1-t}) \leq t \JJ_i \qty(\frac ut) = t^{1 - p_i} \JJ(u). 
	\]
	Letting $t \to 1$, we find $\JJ_i(u + v) \leq \JJ_i(u)$.

	Similarly, we have
	\[
	\JJ_i(u) = \JJ_i(u + v - v) = \JJ_i \qty(t \frac{ u+ v}{t} + (1-t) \frac{-v}{1-t}) \leq t \JJ_i\qty(\frac{u+ v}{t}) = t^{1 - p_i} \JJ_i(u + v), 
	\]
	and letting $t \to 1$ we obtain $\JJ_i(u) \leq \JJ_i(u+v)$, so $\JJ_i(u) = \JJ_i(u+v)$, so $\JJ(u) = \JJ(u + v)$. 
\end{proof}

\begin{recap}
	Let $\XX$ be a Banach space and let $U \subseteq \XX$ be a closed subspace of $\XX$. Then $U$ is called \emph{complemented} in $\XX$ if there exists a closed subspace $V \subseteq \XX$ such that $\XX = U \oplus V$.

	In general, it is difficult to determine which closed subspaces of $\XX$ are complemented. However, it is known that all \textbf{finite-dimensional} subspaces are complemented. 
\end{recap}
\begin{lemma} \label{lem:regulariser_coercive}
	Suppose $\JJ$ is proper, convex, and satisfies the conditions of \cref{lem:null_space_subspace}. Suppose also that:
	\begin{enumerate}[(i)]
		\item $\dim \Nul(\JJ) < \infty$ (so that $\XX = \Nul(\JJ) + \XX_0$ for some closed subspace $\XX_0$) and $\JJ$ is coercive on $\XX_0$;
		\item $\Nul(A) \cap \Nul(\JJ) = \qty{0}$. 
	\end{enumerate}

Then the function $\Phi_\alpha(u) \ceq \frac12\norm{Au - f}^2 + \alpha \JJ(u)$ is coercive on $\XX$ for any $\alpha > 0$. 
\end{lemma}

\begin{proof}
	Let $(u_j) \subseteq \XX$ be a sequence such that $(\Phi_\alpha(u_j))$ is bounded. We will prove that $(u_j)$ is bounded.

	Decompose every $u_j$ as $u_j = u_j^0 + u_j^{\Cal N}$ with $u_j^0 \in \XX_0$ and $u_j^{\Cal N} \in \Nul(\JJ)$. Now, since $(\Phi_\alpha(u_j))$ is bounded, the sequence $(\JJ(u_j)) = (\JJ(u_j^0))$ is bounded as well, and by coercivity of $\JJ$ on $\XX^0$ we conclude that $(u_j^0)$ is bounded.

	Now define $\tilde A \ceq A\restr_{\Nul(\JJ)}$. Since $\Nul(A) \cap \Nul(\JJ) = \qty{0}$, $\tilde A$ has an inverse on $A \Nul(\JJ)$, and since $\dim A\Nul(\JJ) < \infty$, that inverse is bounded. Therefore we find
	\begin{align*}
		\norm{u_j^{\Cal N}} &= \norm{\tilde A^{-1} ( A u_j^{\Cal N})} \leq C \norm{\tilde A u_j^{\Cal N}} = C \norm{\tilde A u_j - f - (A u_j^0 - f)} \leq C \qty(\norm{Au_j - f} + \norm{A} \norm{u_j^0} + \norm{f}). 
	\end{align*}
	Since $\Phi_\alpha(u_j)$ is bounded, $\norm{Au_j - f}$ is also bounded, and the other terms are also all bounded, so we conclude that $(u_j^{\Cal N})$ is bounded, and therefore that $(u_j)$ is bounded. 
\end{proof}

\begin{theorem}
	Let $\XX, \YY$ be Banach spaces with topologies $\tau_\XX, \tau_\YY$. Assume that:
	\begin{enumerate}[(a)]
		\item bounded sequences in $\XX$ have $\tau_\XX$-convergent subsequences;
		\item $\JJ\colon \XX \to [0, \infty]$ is proper, convex, $\tau_\XX$-LSC and satisfies the assumptions of \cref{lem:regulariser_coercive};
		\item $A$ is continuous w.r.t.\ $\tau_\XX$ and $\tau_\YY$;
		\item $\norm{\cdot}_\YY$ is $\tau_\YY$-LSC. 
	\end{enumerate}

Then:
\begin{enumerate}
	\item There exists a $\JJ$-minimising solution $u_\JJ\D$ of the equation $Au = f$;
	\item For any $\alpha > 0$, $f \in \YY$ there exists a minimiser
	\[
 	u_\alpha = R_\alpha f \in \argmin \frac12 \norm{Au - f}^2 + \alpha \JJ(u). 
	\]
\end{enumerate}
\end{theorem}

\begin{proof}
	\begin{enumerate}
		\item Let $\LLL$ be the set of least-squares solutions and $\mu \ceq \inf\qty{\norm{Au - f} \mid u \in \XX}$, then we can write
		\[
		\LLL = \qty{u \in \XX : \norm{Au - f} \leq \mu}. 
		\]
		Since $\norm{\cdot}_\YY$ is $\tau_\YY$-LSC and $A \colon \tau_\XX \to \tau_\YY$ is continuous, we have by \cref{lem:lsc_closed_sets} that $\LLL$ is $\tau_\XX$-closed.

		Now consider the problem 
		\[
		\inf_{u \in \LLL} \JJ(u) = \inf_{u \in \XX} \JJ(u) + \chi_\LLL(u). 
		\] 
		By assumption there exists $u \in \LL$ with $\JJ(u) < \infty$, and the objective function $\JJ + \chi_\LL$ is bounded from below (by 0). Using similar arguments as in the previous lemma (???), it can be shown that it is coercive. Finally, characteristic functions of closed sets are LSC, so $\chi_\LLL$ and $\JJ$ are both $\tau_\XX$-LSC, and therefore their sum is $\tau_\XX$-LSC as well. By the direct method (\cref{thm:direct_method}), we conclude that a $\JJ$-minimising solution exists.

		\item The objective function $\Phi_\alpha$ is coercive by the previous lemma, and also bounded from below. It is easily seen that $\Phi_\alpha$ is $\tau_\XX$-LSC, and using the direct method we conclude that $\Phi_\alpha$ has a minimiser. 
	\end{enumerate}
\end{proof}
